Xor & Some Final analysis

### 2021-09-14 analysis/xor-some_final.Rmd
fixed slope coeff. computation, added hypotheses checks

```{r}
model_SI %>% spread_draws(b_Intercept, b_prior, b_competence, b_relevance,
                          b_main_typexor, `b_prior:competence`,
                          `b_prior:relevance`, `b_competence:relevance`,
                          `b_prior:main_typexor`, `b_competence:main_typexor`,
                          `b_relevance:main_typexor`, `b_prior:competence:relevance`, 
                          `b_prior:competence:main_typexor`, `b_prior:relevance:main_typexor`,
                          `b_competence:relevance:main_typexor`, 
                          `b_prior:competence:relevance:main_typexor`) %>% 
  mutate(
    prior_xor = b_prior + b_main_typexor + `b_prior:main_typexor`,
    prior_some = b_prior,
    competence_xor = b_competence + b_main_typexor + `b_competence:main_typexor`,
    competence_some = b_competence,
    relevance_xor =  b_relevance + b_main_typexor + `b_relevance:main_typexor`,
    relevance_some = b_relevance,
    prior_some_vs_xor = -b_main_typexor - `b_prior:main_typexor`,
    comp_some_vs_xor =  -b_main_typexor - `b_competence:main_typexor`,
    rel_some_vs_xor =  -b_main_typexor - `b_relevance:main_typexor`
  ) -> model_SI_posteriors

# check P that the effects are positive / negative / no effect present
model_SI_posteriors %>% select(prior_xor, prior_some, 
                               competence_xor, competence_some,
                               relevance_xor, relevance_some) %>%
  gather(key, val) %>%
  group_by(key) %>% mutate(positive = mean(val > 0.05),
                           negative = mean(val < -0.05),
                           no = mean(val %>% between(-0.05, 0.05))) %>%
  summarise(positive_eff = mean(positive),
            negative_eff = mean(negative),
            no_eff = mean(no))

```

@@

Since we want to address a conjunctive hypothesis, we check if all three contrasts of interest within a trigger are credibly different from 0. (?)
```{r}
# which models are the bayes factors computed on??
```

>>>>

```{r}
model_SI %>% spread_draws(b_Intercept, b_prior, b_competence, b_relevance,
                          b_main_typexor, `b_prior:competence`,
                          `b_prior:relevance`, `b_competence:relevance`,
                          `b_prior:main_typexor`, `b_competence:main_typexor`,
                          `b_relevance:main_typexor`, `b_prior:competence:relevance`, 
                          `b_prior:competence:main_typexor`, `b_prior:relevance:main_typexor`,
                          `b_competence:relevance:main_typexor`, 
                          `b_prior:competence:relevance:main_typexor`) %>% 
  mutate(
    prior_xor = b_prior + `b_prior:main_typexor`,
    prior_some = b_prior,
    competence_xor = b_competence + `b_competence:main_typexor`,
    competence_some = b_competence,
    relevance_xor =  b_relevance + `b_relevance:main_typexor`,
    relevance_some = b_relevance
  ) -> model_SI_posteriors

# check P that the effects are positive / negative / no effect present
posterior_hypotheses <- model_SI_posteriors %>% 
  select(prior_xor, prior_some, 
         competence_xor, competence_some,
         relevance_xor, relevance_some) %>%
  gather(key, val) %>%
  group_by(key) %>% mutate(positive = mean(val > 0.05),
                           negative = mean(val < -0.05),
                           no = mean(val %>% between(-0.05, 0.05))) %>%
  summarise(positive_eff = mean(positive),
            negative_eff = mean(negative),
            no_eff = mean(no))
posterior_hypotheses
```

@@

We want to address a conjunctive hypothesis, one triplet for each trigger word, namely:

1. the slope of 'competence' is positive
2. the slope of 'prior' is negative
3. the slope of 'relevance' is positive

We judge there to be strong evidence for positivity of a slope variable $\beta_X$, if the posterior probability $P(\beta_X > \delta \mid D)$ is at least $.95$, for $\delta = 0.05$ the parameter that defines our 'region of practical equivalence'.
A posterior odds ratio of at least $\frac{.95}{.05} = 19$ corresponds to a Bayes factor of at least 19 when prior odds are 1.

The binary test of conformity with the theoretical predictions therefore is:
```{r}
test_conjunction_of_all_hypotheses <-  function(posterior_hypotheses) {
  posterior_hypotheses %>% 
    mutate(hypothesis_true = case_when(
      key == 'competence_some' ~ positive_eff > 0.95,
      key == 'competence_xor'  ~ positive_eff > 0.95,
      key == 'prior_some' ~ negative_eff > 0.95,
      key == 'prior_xor'  ~ negative_eff > 0.95, 
      key == 'relevance_some' ~ positive_eff > 0.95,
      key == 'relevance_xor'  ~ positive_eff > 0.95
    )) %>% 
    pull(hypothesis_true) %>% all()
}
# applied to the pilot data
test_conjunction_of_all_hypotheses(posterior_hypotheses)
```

## Experimenting with multiple regression

```{r}
dummy_data <- tribble(
  ~main, ~REL, ~target,
  "some", 0, 4,
  "some", 1, 6,
  "xor", 0, 0,
  "xor", 1, 12
)
# check that the slope of "REL" for "xor" is 12
# this is calculated as betat_REL + beta_mainxor:REL
# importantly: the intercept adjustment beta_mainxor doesn't come in!
lm(target ~ main * REL, dummy_data)
```
